---
title: "RWorksheet_Pineda#4b.Rmd"
output: pdf_document
date: "2023-11-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
```{r}
VectorA <- c(1,2,3,4,5)
  matrixA <- matrix(0,nrow = 5, ncol = 5)
  for(e in 1:5)
  for(f in 1:5)
  {
    matrixA[e,f] <- abs(VectorA[e]-VectorA[f])
  }
  matrixA
```

#2
```{r}
  for(e in 1:5)
  {
  cat(paste0("\"",rep("*",e),"\""),"\n")
  }
```

#3 
```{r}
    User_Input <- as.integer(readline("Enter starting number for Fibonacci Sequence: ")) 
    x <- User_Input
    y <- 0
    
    cat("Fibonacci Sequence starting number from", User_Input, ":\n")
  repeat {
    NumNext <- x + y
    if (NumNext > 500){
      break
    }
    cat(NumNext, " ")
    x <- y
    y <- NumNext
    }
```
#4
```{r}
DataPrevious <- read.csv("DataHousehold.csv")
head(DataPrevious)
```
#4.b
```{r}
Males <- DataPrevious[DataPrevious$Gender == "M",]
Males

Females <- DataPrevious[DataPrevious$Gender == "F",]
Females

NumofMales <- nrow(Males)
NumofMales

NumofFemales <- nrow(Females)
NumofFemales
```

#4.c
```{r}
MaleFemTotal <- table(DataPrevious$Gender)
barplot(MaleFemTotal,
        main = "Number of Males and Females",
        xlab = "Gender",
        ylab = "Count",
        col = c("pink", "blue"),
        legend.text = rownames(MaleFemTotal),
        beside = TRUE)
```

#5
```{r}
SpendingData <- data.frame(Category = c("Food", "Electricity", "Savings", "Miscellaneous"), Value = c(60, 10, 5, 25))

SpendingData$Percentage <- SpendingData$Value / sum(SpendingData$Value * 100)

colors <- c("blue", "green", "yellow", "gray")

pie(SpendingData$Value,
    labels = paste(SpendingData$Category,"(",SpendingData$Percentage,"%)"),
    col = colors,
    main = "Monthly Income Spending of Dela Cruz Family")

legend("topright", SpendingData$Category, fill = colors)
```

#6
```{r}
data(iris)
```

#6.a
```{r}
str(iris)

#The dataset contains information about iris flowers
#It contains information on the length and width of the sepal as well as the length and width of the petal for 150 distinct iris flowers.
#It also keeps track of the iris species to which each flower belongs.
#The dataset contains three species:setosa, versicolor, and virginica
```
#6.b
```{r}
MeanofFlowers <- colMeans(iris[,1:4])
MeanofFlowers
```

#6.c
```{r}
Species <- table(iris$Species)
NameofSpecies <- c("Setosa", "Versicolor", "Virginica")

pie(Species,
    labels = NameofSpecies,
    col = c("cyan", "navy", "coral"),
    main = "Species Distribution in Iris Dataset")

legend("topright", legend = levels(iris$Species), fill = c("cyan", "navy", "coral"),)
```

#6.d
```{r}
iris
SetosaSubset <- iris[iris$Species == "setosa",]
SetosaSubset

VersicolorSubset <- iris[iris$Species == "versicolor",]
VersicolorSubset

VirginicaSubset <- iris[iris$Species == "virginica",]
VirginicaSubset

tail(SetosaSubset)
tail(VersicolorSubset)
tail(VirginicaSubset)
```

#6.e
```{r}
plot(iris$Sepal.Length, iris$Sepal.Width,
  xlab = "Sepal Lenght",
  ylab = "Sepal Width", 
  main = "Iris Dataset", sub = "Sepal Width and Length",
  pch = as.numeric(iris$Species), col = as.numeric(iris$Species))
  
legend("topright", legend = levels(iris$Species),
  pch = 1:3, col = 1:3,
  title = "Species")
```

#6.f
#The scatterplot shows how different species of iris blooms differ in terms of speal length and width.
#Setosa flowers have short spela lengths and wide sepla width. They are gathered in the plot's upper left corner.
#The sepal length and width of Versicolor blooms are ordinary. They are in the center.
#Virgininca flowers often have lengthy speal lengths and shorter sepal widths. They establish a group in the appropriate location.
#The graphic clearly shows the differences in sepal length and width between the three iris species.

#7
```{r}
library(readxl)
Alexa <- read_excel("alexa_file.xlsx")
Alexa
```
#7.a
```{r}
Alexa$variation <- gsub("Black Dot", "BlackDot", Alexa$variation)
Alexa$variation <- gsub("Black Plus", "BlackPlus", Alexa$variation)
Alexa$variation <- gsub("Black Show", "BlackShow", Alexa$variation)
Alexa$variation <- gsub("Black Spot", "BlackSpot", Alexa$variation)

Alexa$variation <- gsub("White Dot", "WhiteDot", Alexa$variation)
Alexa$variation <- gsub("White Plus", "WhitePlus", Alexa$variation)
Alexa$variation <- gsub("White Show", "WhiteShow", Alexa$variation)
Alexa$variation <- gsub("White Spot", "WhiteSpot", Alexa$variation)

Alexa
```
#7.b
